---
title: "Homework 4"
author: "Yitao Tian"
date: "`r Sys.Date()`"
output: 
    html_document: 
        toc: true
        toc_float: true
        theme: cerulean
---
```{r setup, include=FALSE}
#knitr::opts_chunkset(echo = TRUE)
suppressMessages(library(tidyverse))
suppressMessages(library(dplyr))
```

# Question 1
## 1(a)
```{r 1a}
parsum <- function(x, n) {
    partial <- 0
    for (i in 1:n) {
       partial <- partial + (exp(-x) * x^i) / factorial(i)
    }
    return(partial)
}
parsum(x=10, n=15)
```

## 1(b)
```{r 1b}
Printchar <- function(Lst) {
   for (item in Lst) {
      if (is.character(item)) {
        print(item)
      }
   }
}
Printchar(Lst = list("A", 2, "B", 4, "ANDY"))
```

## 1(c)
```{r 1c}
series <- function(x, n) {
   partial <- 1
   for (i in 1:n) {
    partial <- partial + (x^i) / (i)
   }
   return(partial)
}
series(x=2, n=5)
```

# Question 2
## 2(a)
```{r 2a}
restaurant <- read.table(
    "X:/Downloads - Data Drive/Restaurant.txt",
    header=TRUE
)
datatable <- xtabs(
    formula = Count ~ (Age_Group + Food_preference),
    data = restaurant
)
datatable
```

## 2(b)
```{r 2b}
food_pref <- margin.table(
    x = datatable,
    margin = c("Food_preference")
)
(food_pref[["Fish"]] + food_pref[["Steak"]]) / sum(food_pref)
```

## 2(c)
```{r 2c}
age <- prop.table(
    x = datatable,
    margin = c("Food_preference")
)
age[, "Fish"]
```

## 2(d)

Null Hypothesis: no relation

Alternative Hypothesis: there is a relation
between Food preference and Age group

Alpha: 0.05
```{r 2d}
chisq <- chisq.test(datatable)
chisq
```

The p-value of this test was 0.000719, which is less than the alpha of 0.05.

Therefore, we have sufficient evidence to reject the null hypothesis,
and conclude that there is a relation between Food preference and Age group for this sample.

## 2(e)
```{r 2e}
round(chisq$expected, 0)
chisq$observed
```
- [x] There are two categorical variables being compared: Food preference and Age group.
- [x] There are a minimum of 10 observations per combination of categories (min. 12).
- [x] The sample was randomly selected ("A survey of 736 randomly chosen customers...").
- [x] The sample size is greater than 50 (sample size: 736).
- [x] The items in the samples are independent.

## 2(f)
```{r 2f}
mosaicplot(
    datatable,
    shade = TRUE,
    xlab = "Age Group",
    ylab = "Food Preference"
)
```

More adults and seniors dine here than children.

Seniors eat more pasta than kids and adults.

Kids eat more veggies and fish than adults and seniors.

Kids eat the least steak out of all age groups.

Seniors eat the least veggies out of all age groups.

# Question 3
## 3(a)
```{r 3a}
identification <- array(
    data=c(132, 176, 127, 42, 6, 12, 172, 129, 130, 56, 4, 15),
    dim=c(3, 2, 2),
    dimnames=list(
        "Party Identification" = as.factor(c("Democrat", "Republican", "Independent")),
        "Race" = as.factor(c("White", "Black")),
        "Gender" = as.factor(c("Female", "Male"))
    )
)
identification
```

## 3(b)
```{r 3b}
margin.table(
    identification,
    margin = c("Race", "Party Identification")
)
```

## 3(c)

Null Hypothesis: no association

Alternative Hypothesis: there is an association between Race and Party Identification.

Alpha: 0.05
```{r 3c}
chisq.test(as.matrix(identification))
```

Since the Chi-squared test resulted in a p-value of less than 2.2e-16
for the given probabilities, which is itself less than Alpha,
we have sufficient evidence to reject the null hypothesis
and conclude that there is an association between Race and Party Identification.

## 3(d)
```{r 3d}
prop.table(
    identification,
    margin = c(2, 3)
)[2,1,]
```