---
title: "Homework2"
author: "Yitao Tian"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(tidyverse))
library(dplyr)
```

# Question 1
## (a)
```{r 1a}
newdata <- read.csv("X:/Downloads - Data Drive/Health.csv")
Subdata <- filter(newdata, newdata$Stress_Level == "Medium") %>%
  select(-X) %>% 
  select_if(is.numeric) %>%
  sapply(quantile, probs=c(.25,.75)) %>% 
  print
```
## (b)
```{r 1b}
newdata %>%
  aggregate(by=list(.$Stress_Level), FUN=mean) %>% 
  select(Group.1,Weight)
```
# Question 2
```{r 2}
collegedata0708 <- read.csv("X:/Downloads - Data Drive/MERGED2007_08_PP.csv",
                            na=c("NULL","PrivacySuppressed")) %>%
  as_tibble() %>% 
  filter(ICLEVEL==1 &
           REGION==6 &
           MAIN==1) %>%
  mutate(ratio=MD_EARN_WNE_P10/TUITIONFEE_IN) %>% 
  select(INSTNM, STABBR, CITY, ratio) %>%
  arrange(desc(ratio)) %>% 
  print(n=25, width=Inf)
```

# Question 3
## (a)
```{r 3a}
library(readxl)
crimedata <- read_excel("X:/Downloads - Data Drive/table-1.xls",
                        range= "A4:V24")
crimedata[2,1]="2001"
crimedata[19,1]="2018"
cnames <- c("Year","Pop","Vc","Vcr","Manm","Manmr","Rrd","Rrdr","Rld","Rldr","Rob","Robr","Aa","Aar","Pc","Pcr","Bur","Burr","Lt","Ltr","Mvt","Mvtr")
crimedata <- setNames(crimedata,cnames)
aes <- aes(x=Year,y=Vcr)
labs <- labs(x="Time",y="Violent Crime Rate")
title <- ggtitle("The violent crime rate versus time")

ggplot(crimedata, aes) +
  geom_point() +
  geom_line(aes(group=1)) +
  labs +
  title
```
## (b)
```{r 3b}
labs <- labs(x="Time",y="Violent Crime Rate")
title <- ggtitle("The rates of each type of violent crime")

crimedata %>% 
  select("Year","Vcr","Manmr","Rrdr","Rldr","Robr","Aar") %>% 
  pivot_longer(cols=c("Vcr","Manmr","Rrdr","Rldr","Robr","Aar"),
               names_to="Var",
               values_to="Val") %>%
  ggplot(aes(x=Year,y=Val,color=Var)) +
  geom_point() +
  geom_line(aes(group=Var)) +
  labs +
  title
```
## (c)
```{r 3c}
aes <- aes(x=Year, y=Pcr)
labs <- labs(x="Time", y="Property crime rate")
title <- ggtitle("The Property crime rate versus time")

crimedata %>%
  ggplot(aes) +
  geom_point() +
  geom_line(aes(group=1)) +
  labs +
  title
```
## (d)
```{r 3d}
labs <- labs(x="Time",y="Property crime rate")
title <- ggtitle("The Property crime rate versus time")

crimedata %>% 
  select(Year, Burr, Ltr, Mvtr, Pcr) %>% 
  pivot_longer(cols=c("Burr", "Ltr", "Mvtr", "Pcr"),
               names_to="Var",
               values_to="Val") %>% 
  ggplot(aes(x=Year,y=Val,color=Var)) +
  geom_point() +
  geom_smooth(formula=y~x) +
  labs +
  title
```
## (e)
It seems that each type of crime (whether it's violent crime or property crime)
has been steadily decreasing over the last two decades.

For violent crime, the types of violent crime in descending order of rate
is assault, manslaughter, rape (legacy definition), robbery, and rape (updated).

For property crime, the types of property crime in descending occurence rate
is burglary, larceny-theft, and motor vehicle theft.
