---
title: "Homework 3"
author: "Yitao Tian"
date: "`r Sys.Date()`"
output: 
    html_document: 
        toc: true
        toc_float: true
        theme: cerulean
---

```{r setup, include=FALSE, message=FALSE}
library(knitr)
# knitr::opts_chunkset(echo = TRUE)
# install.packages("httpgd")
library(tidyverse)
library(dplyr)
library(ggplot2)
```

# Question 1
## (a)
```{r 1a}
require(ggplot2)

efficiency <- factor(mpg$cty >= 20)
levels(efficiency) <- list("high"="TRUE", "low"="FALSE")

newdata <- cbind(mpg, efficiency)
```

## (b)
```{r 1b}
require(ggplot2)

drv1 <- as.factor(mpg$drv)
levels(drv1) <- list(
    "front-wheel drive"="f",
    "rear-wheel drive"="r",
    "4wd"="4"
)

mpg %>%
    ggplot(aes(x=cty, y=displ, color=drv1)) +
    geom_point() +
    labs(
        title="City mpg vs Engine Displacement",
        x="City Miles per gallon",
        y="Engine Displacement",
        color="Type of Drive Train"
    ) +
    scale_color_manual(
        labels=c("front-wheel drive", "rear-wheel drive", "4wd"),
        values=c("blue", "green", "red")
    )
```

Front-wheel drives have smaller engine displacements than four-wheel drives, which in turn have smaller enginge displacements than rear-wheel drives.

## (c)
```{r 1c}
mpg %>%
    ggplot(aes(sample = hwy)) +
    stat_qq() +
    stat_qq_line()
shapiro.test(mpg$hwy)
```

Null Hypothesis: hwy variable is normally distributed

Choose alpha level to be 0.05

The Shapiro-Wilk test results in a p-value of 2.999e-06

The p-value is less than alpha, so i reject the null hypothesis.

There is evidence hwy data are not normally distributed.

# Question 2
## (a)
```{r 2a}
require(tibble)
require(readr)

d <- read_csv("X:/Downloads - Data Drive/Sales_data.csv")

# Line plot of total profit
d %>%
    ggplot(aes(x = month_number, y = total_profit)) +
    geom_point() +
    geom_line(aes(color = "red", group = 1)) +
    labs(
        title = "company sales data of last year",
        x = "Month number",
        y = "Profit in dollars"
    ) +
    scale_x_continuous(breaks = 1:12)
```

Sales on an upward trend as the year progresses.

Sales are at its highest in November, and second highest in August.

Sales are at its lowest in February.

## (b)
```{r 2b}
require(tidyr)
# Line chart of sales for each product
d %>%
    select(-c(total_units,total_profit)) %>%
    pivot_longer(
        cols = -month_number,
        names_to = "Product",
        values_to = "Unit"
    ) %>%
    ggplot(aes(
        x = month_number,
        y = Unit,
        color = Product
    )) +
    geom_point() +
    geom_line(aes(color = Product, group = Product)) +
    labs(
        title = "Company sales data by product",
        x = "Month number",
        y = "Units"
    ) +
    scale_x_continuous(breaks = 1:12)
```

The products in order of popularity are:

Bathing soap, toothpaste, facecream, shampoo, and moisturizer.

Bathing soap and toothpaste sales trend upward as the year goes on.

People have bought more than twice as much bathing soap in December than in February.

## (c)
```{r 2c}
# Bar chart of facewash and face cream sales
d %>%
    select(month_number,facecream,facewash) %>% 
    pivot_longer(
        cols = -month_number,
        names_to = "Product",
        values_to = "Unit"
    ) %>%
    ggplot(aes(
        x = month_number,
        y = Unit,
        fill = Product
    )) +
    geom_bar(
        position = "dodge",
        stat = "identity"
    ) +
    labs(
        title = "Comparison between facecream and facewash sales",
        x = "Month Number",
        y = "Units"
    ) +
    scale_x_continuous(breaks = 1:12)
```

Face cream consistently outsells face wash.

Often, face cream sales are twice as much as facewash sales.

# Question 3
```{r 3}
# Function definition
tmpFn <- function(x) {
    ifelse(x < 0, (x^2) + (2 * x) + 3,
        ifelse(x < 2, x+3, (x^2)+(4*x)-7))
}
# Input Vector
input <- seq(
    from = -3,
    to = 3,
    length.out = 50
)
# Dataframing
df <- data.frame(cbind(input, tmpFn(input)))
# Plotting
ggplot(df, aes(x = input, y = V2)) +
    geom_point()
```
